Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and Multiple Kernel Learning

### 2016-11-25 paper.tex

With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid. This step can also be time consuming, especially when dealing with data in a structured form.

In this paper, we propose a new approach to parameter selection that, based on sub-sampling and Multiple Kernel Learning, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.

@@

\subsection{Multiple Kernel Learning (MKL)}
\label{MKL}
MKL \cite{Bach2004,Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
$
	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
$
with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

>>>>

With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid. This step can also be time consuming, especially when dealing with data in a structured form.

In this paper, we propose a new approach to parameter selection that, based on sub-sampling and MKL, is able to speedup the parameter selection phase by orders of magnitude on real-world datasets.

@@

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Bach2004,Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
$
	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
$
with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.
